\documentclass{article}
\usepackage{a4wide}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Simon Dobnik}
\lhead{List of Publications}
\rfoot{Page \thepage}
\begin{document}

\section*{List of Publications}






\subsection*{Peer-reviewed original articles}

\begin{itemize}
\item \textbf{Simon Dobnik} and Robin Cooper. 2017. Interfacing language, spatial perception and cognition in Type Theory with Records. Journal of Language Modelling, 5(2):1–29.



\item Robin Cooper, \textbf{Simon Dobnik}, Shalom Lappin, and Staffan Larsson. 2015. Probabilistic type theory and natural language semantics. Linguistic Issues in Language Technology (LiLT), 10(4):1–43.
\end{itemize}
\subsection*{Peer-reviewed conference contributions}
\begin{itemize}
\item \textbf{Simon Dobnik}, Mehdi Ghanimifard, and John D. Kelleher. 2018. Explorations of functionally- and geometrically-biased spatial relations with neural language models. In Proceedings of the First International Workshop on Spatial Language Understanding (SpLU 2018) at NAACL-HLT 2018, pages 1–10, New Orleans, Louisiana, USA. North American Chapter of the Association for Computational Linguistics: Human Language Technologies

\item \textbf{Simon Dobnik} and John D. Kelleher. 2017. Modular mechanistic networks: On bridging mechanistic and phenomenological models with deep neural networks in natural language processing. In Simon Dobnik and Shalom Lappin, editors. 2017. CLASP Papers in Computational Linguistics: Proceedings of the Conference on Logic and Machine Learning in Natural Language (LaML 2017), Gothenburg, 12–13 June, volume 1. pages 1–11

\item \textbf{Simon Dobnik} and Amelie \AA stbom. 2017. (Perceptual) grounding as interaction. In Proceedings of Saardial – Semdial 2017: The 21st Workshop on the Semantics and Pragmatics of Dialogue, pages 17–26, Saarbrücken, Germany


\item Mehdi Ghanimifard and \textbf{Simon Dobnik}. 2017. Learning to compose spatial relations with grounded neural language models. In Proceedings of IWCS 2017: 12th International Conference on Computational Semantics, pages 1–12, Montpellier, France. Association for Computational Linguistics

\item \textbf{Simon Dobnik} and John D. Kelleher. 2016. A model for attention-driven judgements in type theory with records. In JerSem: The 20th Workshop on the Semantics and Pragmatics of Dialogue, volume 20, pages 25–34, New Brunswick, NJ USA.


\item \textbf{Simon Dobnik} and John D. Kelleher. 2014. Exploration of functional semantics of prepositions from corpora of descriptions of visual scenes. In Proceedings of the Third V\&L Net Workshop on Vision and Language, pages 33–37, Dublin, Ireland. Dublin City University and the Association for Computational Linguistics.

\item \textbf{Simon Dobnik} and John D. Kelleher. 2013. Towards an automatic identification of functional and geometric spatial prepositions. In Proceedings of PRE-CogSsci 2013: Production of referring expressions – bridging the gap between cognitive and computational approaches to reference, pages 1–6, Berlin, Germany.
\end{itemize}
\subsection*{Peer-reviewed books and book chapters}


\begin{itemize}
\item \textbf{Simon Dobnik}. 2009. Teaching mobile robots to use spatial words. PhD thesis, University of Oxford: Faculty of Linguistics, Philology and Phonetics and The Queen’s College, Oxford, United Kingdom, September 4.

\end{itemize}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% mode: flyspell
%%% TeX-master: t
%%% TeX-PDF-mode: t
%%% coding: utf-8
%%% ispell-local-dictionary: "british"
%%% End:
